# Power Analysis Calculation

Functions to generate treatment vector and outcome vector. Outcome drawn from a binomial distribution with probability `prob_click` to represent the probability that a user clicked the ad. 

```{r randomization}
randomize <- function(units_per_group){
  assignment_vector <- rep(c(0, 1), each=units_per_group)
  sample(assignment_vector)
}

randomize_effect <- function(n, prob_click){
  # rnorm(n, mean=prob_click, sd=sqrt(prob_click * (1 - prob_click)))
  effect_vector <- rbinom(n, 1, prob_click)
  effect_vector
}
```

`industry_ctr` is the 2021 average click through rate for Facebook ads in the education industry. Let's start with a hypothetical treatment effect of 0.014. This represents a 200% increase in CTR. `make_data` is a function to generate fake data with `num_subjects` participants and an ATE of `effect_size`.

```{r using industry ctr}
industry_ctr <- 0.0073
hyp_effect_size <- 0.014

make_data <- function(num_subjects, effect_size){
  d <- data.table(id = 1:num_subjects)
  d[ , treatment := randomize(.N/2)]
  
  d[ , clicked_control := randomize_effect(.N, industry_ctr)]
  d[ , clicked_treatment := randomize_effect(.N, industry_ctr + effect_size)]
  
  d[ , clicked := ifelse(treatment == 0, clicked_control, clicked_treatment)]
}
```

Generating sample data with 1000 participants. 

```{r generate fake data}
d <- make_data(1000, hyp_effect_size)
head(d)
```
ATE for this sample. 

```{r ATE of the fake data}
d[ , mean(clicked), keyby=treatment][, diff(V1)]
```

Below is a function to run RI and calculate p_values. 

```{r run RI and calculate p-values}
get_pvalues <- function(n, effect_size, num_replications){
  p_values <- NA
  
  for (i in 1:num_replications){
    data <- make_data(n, effect_size)
    p_values[i] <- data[ , t.test(clicked ~ treatment)]$p.value
  }
  p_values 
}
```

Generating fake p_value distribution from data `d`. 

```{r generate p-value distribution}
p_value_dist <- get_pvalues(1000, hyp_effect_size, 1000)
```

Plotting the p_value distribution. 

```{r plot results}
ggplot() + 
  aes(p_value_dist) + 
  geom_histogram() + 
  labs(
    title="Distribution of p-values",
    x = 'P-values from repeated t-tests'
  )
```
Power of our test:

```{r statistical power}
t_test_rejects <- mean(p_value_dist < 0.05)
t_test_rejects
```

Below we are simulating different treatment effects and different treatment sizes, and printing the power of our test for each plausible scenario. 

```{r simulation with different treatment sizes and effects}
sample_per_condition  <- c(100, 1000, 100000, 1000000) 
hypothetical_ctrs <- c(industry_ctr * 0.1, industry_ctr * 0.3, industry_ctr * 0.4, 
                       industry_ctr * 0.5, industry_ctr * 0.7, industry_ctr * 0.8, 
                       industry_ctr * 0.9, industry_ctr, industry_ctr * 2)

achieved_power <- NA

for (ctr in hypothetical_ctrs){
  for(i in 1:length(sample_per_condition)) { 
    n <- sample_per_condition[i]
    
    p_values <- get_pvalues(n, ctr, 100)
  
    achieved_power[i] <- mean(p_values < 0.05)
  
    cat(
        sprintf(
          'For a treatment effect of %s, a sample size of %.2f, there is power of %.3f\n',
          paste(ctr),
          sample_per_condition[i], 
          achieved_power[i]
          )
      )
  }

  print(ggplot() + 
          aes(x = sample_per_condition, y = achieved_power) + 
          geom_point() + 
          geom_line() + 
          labs(
            title    = paste('Achieved Power for CTR =', ctr), 
            x        = 'Sample Size', 
            y        = 'Achieved Power'
    ))
    
}

```
