```{r}
robust_se <- function(model){
  # get robust standard error
  sqrt(diag(vcovHC(model)))
}

d <- fread(file="../data/fb_ad_data.csv")
```

# Covariate Balance Check
Each covariate appears balanced across the four groups.

```{r covariate balance check}
#Balance check: Averages across control and treatment groups
cov_balance_checks <- d[, mean(clicked) * 100, by=.(group)]

#Balance check: Share of females across control and treatment groups
cov_balance_checks$share_female <- d[, sum(gender == 'female')/(.N), by=.(group)]$V1

#Balance check: Share of males across control and treatment groups
cov_balance_checks$share_male <- d[, sum(gender == 'male')/(.N), by=.(group)]$V1

#Balance check: Share of 18-24 year olds across control and treatment groups
cov_balance_checks$share_18_24 <- d[, sum(age == '18-24')/(.N), by=.(group)]$V1

#Balance check: Share of 25-34 year olds across control and treatment groups
cov_balance_checks$share_25_34 <- d[, sum(age == '25-34')/(.N), by=.(group)]$V1

#Balance check: Share of 35-44 year olds across control and treatment groups
cov_balance_checks$share_35_44 <- d[, sum(age == '35-44')/(.N), by=.(group)]$V1

#Balance check: Share of 45-54 year olds across control and treatment groups
cov_balance_checks$share_45_54 <- d[, sum(age == '45-54')/(.N), by=.(group)]$V1

#Balance check: Share of 55-64 year olds across control and treatment groups
cov_balance_checks$share_55_64 <- d[, sum(age == '55-64')/(.N), by=.(group)]$V1

#Balance check: Share of 65+ year olds across control and treatment groups
cov_balance_checks$share_65 <- d[, sum(age == '65+')/(.N), by=.(group)]$V1

#Balance check: Share of "unknown age" not necessary -- can subtract. 
head(cov_balance_checks)

```

## Visualization/EDA

``` {r}
s <- d[age!='unknown', .(count=length(clicked)), by=.(age,group)]
ggplot(data= s, aes(x=age, y=count, fill=group)) + 
  geom_bar(stat='identity') +
  labs(x='Age Group', y='Count', fill='Ad type') +
  labs(title = "Age distribution, divided by ad assignment type")
```

``` {r}
t <- d[age!='unknown', .(count=length(clicked)), by=.(age, gender)]
ggplot(data= t, aes(x=age, y=count, fill=gender)) + 
  geom_bar(stat='identity') +
  labs(x='Age Group', y='Count', fill='Gender') +
  labs(title = "Age distribution, divided by gender") +
  scale_fill_manual(values = c("#DADAEB", "#9E9AC8", "#6A51A3"))
```

```{r}
u <- d[, .(count=length(clicked)), by=.(group, gender)]
ggplot(data= u, aes(x=group, y=count, fill=gender)) + 
  geom_bar(stat='identity') +
  labs(x='Treatment group', y='Count', fill="Gender") +
  labs(title = "Ad treatment distribution, divided by gender") +
  scale_fill_manual(values = c("#DADAEB", "#9E9AC8", "#6A51A3"))
```

# Covariate Balance Check Against Pilot Study
Mean clicks should look similar across groups for pilot study and full study. Covariates should also look similar.

```{r compare to pilot}
#Read in pilot data
pilot <- fread(file="../data/pilot_data.csv")
setnames(pilot, "Ad name", "group")
setnames(pilot, "Unique clicks (all)", "clicked")

#Balance check: Averages across control and treatment groups for pilot
pilot_balance_checks <- pilot[, 100*sum(clicked)/sum(Reach), by=.(group)]

#Balance check: Share of females across control and treatment groups for pilot
pilot_balance_checks$share_female <- pilot[Gender == 'female', sum(clicked), by=.(group)]$V1/pilot[, sum(clicked), by=.(group)]$V1

pilot_balance_checks
```

# In-Depth Covariate Balance Check using t-test and f-test for randomization
## One hot encoded data
```{r one-hot encode treatment groups}
ad_codes <- c('control', 'visual', 'text', 'text_visual')
ad_groups <- c('control', 'visual treatment', 'text treatment', 'text + visual treatment')
for (i in 1:length(ad_groups)) {
  d[, ad_codes[i] := ifelse(group == ad_groups[i], 1, 0)]
}
```

```{r one-hot encode genders}
genders <- c('female', 'male')
for (i in 1:length(genders)) {
  d[, genders[i] := ifelse(gender == genders[i], 1, 0)]
}
d[, "unknown_gender" := ifelse(gender == "unknown", 1, 0)]
```

```{r one-hot encode ages}
age_codes <- c('age18_24', 'age25_34', 'age35_44', 'age45_54', 'age55_64', 'age65plus')
ages <- c('18-24', '25-34', '35-44', '45-54', '55-64', '65+')
for (i in 1:length(ages)) {
  d[, age_codes[i] := ifelse(age == ages[i], 1, 0)]
}
d[, "unknown_age" := ifelse(age == "unknown", 1, 0)]
```

## Create new treatment labels
- `treated`: Received any treatment (1 or 0)
- `visual` : Any visual treatment (visual treatment only OR text and visual treatment) (1 or 0)
- `text` : Any textual treatment (textual treatment only OR text and visual treatment) (1 or 0)

```{r create any treatment label}
d[, treated := ifelse(test = group != "control", yes = 1, no = 0)]
```

```{r create any visual treatment label}
d[, visual := ifelse(test = group == "visual treatment" | group == "text + visual treatment", yes = 1, no = 0)]
```

```{r create any text treatment label}
d[, text := ifelse(test = group == "text treatment" | group == "text + visual treatment", yes = 1, no = 0)]
```

---

## Randomziation check 

This code uses female, male, unknown gender (omitted/used as constant) and age groups 18-24, 25-34, 35-44, 45-54, 55-64, 65+, and unknown age (omitted/used as constant) to check for covariate randomization.
```{r t-test of variables for randomness}
#Estimate model
m_genderonly_t <- lm(treated ~ female + male,
                     data=d)

m_saturate_trt <- lm(treated ~ female + male + 
                       age18_24 + age25_34 + age35_44 + age45_54 + age55_64 + age65plus,
                     data=d)

#Print results with stargazer
stargazer(m_genderonly_t, m_saturate_trt, 
          se = c(list(robust_se(m_genderonly_t)),
                 list(robust_se(m_saturate_trt))),
          type = 'text')

#Run f-test with same model
anova(lm(treated ~ female + male + age18_24 + age25_34 + age35_44 + age45_54 + age55_64 + age65plus, 
         data=d),
      test = "F")
```

This code uses female (omitted/used as constant), male, unknown gender and age groups 18-24 (omitted/used as constant), 25-34, 35-44, 45-54, 55-64, 65+, and unknown age to check for covariate randomization. It differs from the previous code because of how the lm model choose which covariate to treat as a constant. We choose to see the male and female covariate to see our variables of interest better. While in regression, using the unknown gender and age as constants wouldn't make sense, since this is a randomization test, both modes work.
```{r t-test of variables for randomness with FACTORS}
#Estimate model
m_simple_treat <- lm(treated ~ factor(gender), 
         data=d)

m_saturate_trt <- lm(treated ~ factor(gender) + factor(age), 
         data=d)

#Print results
stargazer(m_simple_treat, m_saturate_trt, 
          se = c(list(robust_se(m_simple_treat)),
                 list(robust_se(m_saturate_trt))),
          type = 'text')

#Run f-test with same model
anova(lm(treated ~ factor(gender) + factor(age), 
         data=d),
      test = "F")
```

---

# Simple model, gender model, saturated model
Without interaction terms and removing unknown age and gender labels
```{r simple, gender, and saturated model}
#Estimate model
simple_m <- d[(gender != "unknown" & age != "unknown"), 
              lm(clicked ~ text + visual + text_visual)]

gender_m <- d[(gender != "unknown" & age != "unknown"), 
                 lm(clicked ~ text + visual + text_visual + female)]

saturated_m <- d[(gender != "unknown" & age != "unknown"), 
                 lm(clicked ~ text + visual + text_visual + female + 
                      age18_24 + age25_34 + age35_44 + age45_54 + age55_64)]
#Print results
stargazer(simple_m, gender_m, saturated_m,
          se = c(list(robust_se(simple_m)), 
                 list(robust_se(gender_m)),
                 list(robust_se(saturated_m))),
          type = 'text')
```