# Create new treatment labels
- `treated`: Received any treatment (1 or 0)
- `visual` : Any visual treatment (visual treatment only OR text and visual treatment) (1 or 0)
- `text` : Any textual treatment (textual treatment only OR text and visual treatment) (1 or 0)

```{r create any treatment label}
d[, treated := ifelse(test = group != "control", yes = 1, no = 0)]
```

```{r create any visual treatment label}
d[, visual := ifelse(test = group == "visual treatment" | group == "text + visual treatment", yes = 1, no = 0)]
```

```{r create any text treatment label}
d[, text := ifelse(test = group == "text treatment" | group == "text + visual treatment", yes = 1, no = 0)]
```

# New treatment labels on click through rate
## What effect does simply getting any treatment at all versus none have on the clickthru rate?
```{r any treatment}
model_treat_at_all <- lm(clicked ~ treated, data = d)
model_treat_at_all
coeftest(model_treat_at_all, vcov = vcovHC(model_treat_at_all, type = "HC0"))
stargazer(model_treat_at_all,
          se=robust_se(model_treat_at_all),
          type="text")
```
As we can see, if given any treatment, it corresponds to a 0.0008 (9.22e-05) increase in the clicked variable, which is an 0.0008 increase in the probability of them clicking, a small yet statistically significant difference. 

## Now let's see what the effect of a visual treatment is.

```{r recieving any visual treatment}
model_visual <- lm(clicked ~ visual, data = d)
model_visual
coeftest(model_visual, vcov = vcovHC(model_visual, type = "HC0"))
stargazer(model_visual,
          se=robust_se(model_visual),
          type="text")
```
Receiving a visual treatment corresponds to a 0.111 (0.009) increase in the probability of someone clicking the ad.

## Now what about a text treatment?
```{r recieving any text treatment}
model_text <- lm(clicked ~ text, data = d)
model_text
coeftest(model_text, vcov = vcovHC(model_text, type = "HC0"))
stargazer(model_text,
          se=robust_se(model_text),
          type="text")
```
Receiving a text treatment corresponds to a 0.061 (0.011) decrease in the probability of someone clicking the ad.

# Individual treatment groups in relation to the control

```{r text treatment only}
model_just_text <- lm(clicked ~ treated, data = d[d$group == "control" | group == "text treatment"])
model_just_text
coeftest(model_just_text, vcov = vcovHC(model_just_text, type = "HC0"))
stargazer(model_just_text,
          se=robust_se(model_just_text),
          type="text")
```

```{r visual treatment only}
model_just_visual <- lm(clicked ~ treated, data = d[d$group == "control" | group == "visual treatment"])
model_just_visual
coeftest(model_just_visual, vcov = vcovHC(model_just_visual, type = "HC0"))
stargazer(model_just_visual,
          se=robust_se(model_just_visual),
          type="text")
```

```{r recieving text and visual treatment only}
model_text_visual <- lm(clicked ~ treated, data = d[d$group == "control" | group == "text + visual treatment"])
model_text_visual
coeftest(model_text_visual, vcov = vcovHC(model_text_visual, type = "HC0"))
stargazer(model_text_visual,
          se=robust_se(model_text_visual),
          type="text")
```

---

# It seems as if the text treatments aren't having as big of an effect. Is adding the visual treatment on top of text more impactful than adding a text treatment on top of visual? 

```{r visual on top of text}
model_add_visual_to_text <- lm(clicked ~ visual, data = d[d$group == "text treatment" | group == "text + visual treatment"])
model_add_visual_to_text
coeftest(model_add_visual_to_text, vcov = vcovHC(model_add_visual_to_text, type = "HC0"))
stargazer(model_add_visual_to_text,
          se=robust_se(model_add_visual_to_text),
          type="text")
```

## Is adding the text treatment on top of visual more impactful than adding a visal treatment on top of text? 

```{r text on top of visual}
model_add_text_to_visual <- lm(clicked ~ text, data = d[d$group == "visual treatment" | group == "text + visual treatment"])
model_add_text_to_visual
coeftest(model_add_text_to_visual, vcov = vcovHC(model_add_text_to_visual, type = "HC0"))
stargazer(model_add_text_to_visual,
          se=robust_se(model_add_text_to_visual),
          type="text")
```

# Let's explore the effect of gender on the clickthru rate.

```{r gender on clicks}
model_gender <- lm(clicked ~ gender, data = d[d$gender != "unknown"])
model_gender
coeftest(model_gender, vcov = vcovHC(model_gender, type = "HC0"))
stargazer(model_gender,
          se=robust_se(model_gender),
          type="text")
```

---

```{r all of the any treatment models}
stargazer(model_treat_at_all, 
          model_visual, 
          model_text, 
          se= c(robust_se(model_treat_at_all), 
                robust_se(model_visual), 
                robust_se(model_text)
                ),
          type="text")
```

```{r individual treatment groups}
stargazer(model_just_text, 
          model_just_visual, 
          model_text_visual,
          se= c(robust_se(model_just_text), 
                robust_se(model_just_visual), 
                robust_se(model_text_visual)
                ),
          type="text")
```

```{r visual on top of text and vice versa}
stargazer(model_add_visual_to_text, 
          model_add_text_to_visual,
          se= c(robust_se(model_add_visual_to_text),
                robust_se(model_add_text_to_visual)
                ),
          type="text")
```

```{r interaction terms models}
# Interact with removed unknown gender and unknown age
interact_m <- d[(gender != "unknown" & age != "unknown"), 
                 lm(clicked ~ textvisual + 
                      text + 
                      visual + 
                      a25_34 + 
                      a35_44 + 
                      a45_54 + 
                      a55_64 +
                      a65plus +
                      male +
                      textvisual * male + 
                      text * male +
                      visual * male)]

# Trying to replicate the stargazer table from the final presentation
interact_all <- d[, 
                 lm(clicked ~ textvisual + 
                      text + 
                      visual + 
                      a25_34 + 
                      a35_44 + 
                      a45_54 + 
                      a55_64 +
                      a65plus +
                      unknown_age +
                      male +
                      unknown_gender +
                      textvisual * male + 
                      text * male +
                      visual * male +
                      textvisual * unknown_gender +
                      text * unknown_gender +
                      visual * unknown_gender)]

stargazer(interact_m, interact_all,
          se = c(
            list(robust_se(interact_m)),
            list(robust_se(interact_all))
            ),
          type = 'text')
```

