# Model exploration

## New treatment labels on click through rate

- `treated`: Received any treatment (1 or 0)
- `visual` : Any visual treatment (visual treatment only OR text and visual treatment) (1 or 0)
- `text` : Any textual treatment (textual treatment only OR text and visual treatment) (1 or 0)

### What effect does simply getting any treatment at all versus none have on the clickthru rate?
```{r any treatment}
model_treat_at_all <- lm(clicked ~ treated, data = d)
model_treat_at_all
coeftest(model_treat_at_all, vcov = vcovHC(model_treat_at_all, type = "HC0"))
stargazer(model_treat_at_all,
          se=robust_se(model_treat_at_all),
          type="text")
```
As we can see, if given any treatment, it corresponds to a 0.0008 (9.22e-05) increase in the clicked variable, which is an 0.0008 increase in the probability of them clicking, a small yet statistically significant difference. 

### Now let's see what the effect of a visual treatment is.

```{r recieving any visual treatment}
model_visual <- lm(clicked ~ visual, data = d)
model_visual
coeftest(model_visual, vcov = vcovHC(model_visual, type = "HC0"))
stargazer(model_visual,
          se=robust_se(model_visual),
          type="text")
```
Receiving a visual treatment corresponds to a 0.111 (0.009) increase in the probability of someone clicking the ad.

### Now what about a text treatment?
```{r recieving any text treatment}
model_text <- lm(clicked ~ text, data = d)
model_text
coeftest(model_text, vcov = vcovHC(model_text, type = "HC0"))
stargazer(model_text,
          se=robust_se(model_text),
          type="text")
```
Receiving a text treatment corresponds to a 0.061 (0.011) decrease in the probability of someone clicking the ad.

## Individual treatment groups in relation to the control

```{r text treatment only}
model_just_text <- lm(clicked ~ treated, data = d[d$group == "control" | group == "text treatment"])
model_just_text
coeftest(model_just_text, vcov = vcovHC(model_just_text, type = "HC0"))
stargazer(model_just_text,
          se=robust_se(model_just_text),
          type="text")
```

```{r visual treatment only}
model_just_visual <- lm(clicked ~ treated, data = d[d$group == "control" | group == "visual treatment"])
model_just_visual
coeftest(model_just_visual, vcov = vcovHC(model_just_visual, type = "HC0"))
stargazer(model_just_visual,
          se=robust_se(model_just_visual),
          type="text")
```

```{r recieving text and visual treatment only}
model_text_visual <- lm(clicked ~ treated, data = d[d$group == "control" | group == "text + visual treatment"])
model_text_visual
coeftest(model_text_visual, vcov = vcovHC(model_text_visual, type = "HC0"))
stargazer(model_text_visual,
          se=robust_se(model_text_visual),
          type="text")
```

---

## Visual on top of text OR text on top of visual?

### Visual on top of text
It seems as if the text treatments aren't having as big of an effect. Is adding the visual treatment on top of text more impactful than adding a text treatment on top of visual? 

```{r visual on top of text}
model_add_visual_to_text <- lm(clicked ~ visual, data = d[d$group == "text treatment" | group == "text + visual treatment"])
model_add_visual_to_text
coeftest(model_add_visual_to_text, vcov = vcovHC(model_add_visual_to_text, type = "HC0"))
stargazer(model_add_visual_to_text,
          se=robust_se(model_add_visual_to_text),
          type="text")
```

### Text on top of visual 
Is adding the text treatment on top of visual more impactful than adding a visal treatment on top of text? 

```{r text on top of visual}
model_add_text_to_visual <- lm(clicked ~ text, data = d[d$group == "visual treatment" | group == "text + visual treatment"])
model_add_text_to_visual
coeftest(model_add_text_to_visual, vcov = vcovHC(model_add_text_to_visual, type = "HC0"))
stargazer(model_add_text_to_visual,
          se=robust_se(model_add_text_to_visual),
          type="text")
```

## Effects of gender on click through rate
Let's explore the effect of gender on the clickthru rate.

```{r gender on clicks}
model_gender <- lm(clicked ~ gender, data = d[d$gender != "unknown"])
model_gender
coeftest(model_gender, vcov = vcovHC(model_gender, type = "HC0"))
stargazer(model_gender,
          se=robust_se(model_gender),
          type="text")
```

---

# Model Exploration Stargazer Tables
Comparing models from Model Exploration section using Stargazer

## New treatment labels
```{r all of the any treatment models}
stargazer(model_treat_at_all, 
          model_visual, 
          model_text, 
          se= c(robust_se(model_treat_at_all), 
                robust_se(model_visual), 
                robust_se(model_text)
                ),
          type="text")
```
## Individual treatment groups
```{r individual treatment groups}
stargazer(model_just_text, 
          model_just_visual, 
          model_text_visual,
          se= c(robust_se(model_just_text), 
                robust_se(model_just_visual), 
                robust_se(model_text_visual)
                ),
          type="text")
```
## Visual on top of text OR Text on top of visual
```{r visual on top of text and vice versa}
stargazer(model_add_visual_to_text, 
          model_add_text_to_visual,
          se= c(robust_se(model_add_visual_to_text),
                robust_se(model_add_text_to_visual)
                ),
          type="text")
```

---

# Model used in the final presentation (updated below)
```{r simple and saturated+interaction models using I()}
# Kevin's code, adapted
simp <- lm(clicked ~ I(group), data=d)
full <- lm(clicked ~ I(group) + I(age) + I(gender) + (I(group) * I(gender)), data=d)
stargazer(simp, full,
          se=c(list(robust_se(simp)),
               list(robust_se(full))), 
          type = "text")
```

---

# Final Model with interaction terms

```{r interaction terms models with different variables}
# Interact with removed unknown gender and unknown age
basic_model <- d[(gender != "unknown" & age != "unknown"), 
                 lm(clicked ~ text_visual + text + visual)]

full_intr_m <- d[(gender != "unknown" & age != "unknown"), 
                 lm(clicked ~ text_visual + text + visual +
                      I(female) +
                      I(age18_24) +
                      I(age25_34) + 
                      I(age35_44) + 
                      I(age45_54) + 
                      I(age55_64) +
                      I(text_visual * female) + 
                      I(text * female) +
                      I(visual * female))]

stargazer(basic_model, full_intr_m,
          se = c(
            list(robust_se(basic_model)),
            list(robust_se(full_intr_m))),
          type = 'text')
```